\vspace{-2cm} Government websites as data: \\ A methodological pipeline with application to the websites of municipalities in the United States

### 2018-09-28 paper/manuscript.tex
addressed two points

The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents produced by governments, public officials, and candidates for office. The most pertinent literature to our research is the e-governance literature, which focuses on the online presence of governments from a usability and public service point of view. For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use, and function, and then hand-codes a set of websites according to these criteria \citep[e.g., ][]{Urban2002,Armstrong2011,Feeney2017}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency. To this end, they analyze a set of Dutch municipalities in which air quality had deteriorated. The authors test whether local governments provide citizens with information about potential complications and solutions associated with this issue. Like most e-government studies, however, this publication does not make any use of automated text analysis.
%Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}. \cite{Lin2011} provide a good example of a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles. The authors estimate the political slant of these entities by counting the frequencies with which politicians of either side are mentioned and determine that blogs are generally more biased. Unfortunately for us, the authors don't go into the details of their text analysis, and offer no information on the acquisition and pre-processing of the data.
%Another well-known example fitting into this area of study is the set of studies conducted by King et al. \citep{KING2013,King2014,KING2017}, in which the authors study censorship by the country's government on its lively blogosphere. However, the authors also provide no information on how their data was collected ``our extensive engineering effort, which we do not detail here for obvious reasons [...]''.

The websites of politicians and their parties have also fallen under scholarly scrutiny. Researchers have found that in order to identify the constituencies, motives, and modes of communication among these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}. \cite{Druckman2009,Druckman2010} rely on the \textit{National Journal} to find the websites, then hand-coded them. \cite{Cryer2017} mentions that she relied on Archive-it, a web service of the Internet Archive. Though the Internet Archive may provide extensive coverage of high profile officials or national governments, we found that its coverage of municipal government websites was sparse and irregular.
\cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress. \cite{Therriault2010} use automated text analysis, and also has the most extensive overview of the associated methodology. However, the division of the website into sections (home page, topics, issues, details) is done by hand. The author acquired the websites from the Library of Congress (which only collected them from legislators who actually consented, and Therriault notes that this causes nonrandom missingness).

@@

% BRUCE HERE

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis. The methods involved in the pipeline include checking the integrity of the site addresses, extracting English language from website contents, identifying document types, and removing boilerplate language. Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government. We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.

We offer several contributions that will be valuable in future research endeavors. First, the data collected in the current study can be used for comparative analysis of US city website contents. Second, the pipeline we present can be used as a set of procedures to follow in gathering large-scale datasets of textual contents from other samples of governments. Third, our findings regarding the effects of mayoral partisanship on city website contents advance the literature on the role of partisan leadership in local government, and reinforce the finding of \citet{gerber2011mayors} that the effects of mayoral partisanship can be best observed through the analysis of domains of government (e.g., website contents) that are not heavily constrained by state or national governments.

>>>>

The existing research that uses scraped websites provides an indication of the theoretical value of empirical analysis of web contents produced by governments, public officials, and candidates for office. The most pertinent literature to our research is the e-governance literature, which focuses on the online presence of governments from a usability and public service point of view. For the most part, research in this category develops a classification scheme to rate websites in terms of accessibility, ease-of-use, and function, and then hand-codes a set of websites according to these criteria \citep[e.g., ][]{Urban2002,Armstrong2011,Feeney2017}. As an example, \cite{grimmelikhuijsen2012developing} study local government websites with the goal of uncovering how they aid the goal of transparency. To this end, they analyze a set of Dutch municipalities in which air quality had deteriorated. The authors test whether local governments provide citizens with information about potential complications and solutions associated with this issue. Like most e-government studies, however, this publication does not make any use of automated text analysis. Branching out of the topic of e-government service provision, \citet{mcnutt2010virtual} uses Canadian government websites to study how well-connected government websites are to non-profits and intergovernmental organizations in different public policy domains.
%Websites have also played a major role in the field of media studies, as scholars have scraped and analyzed the online presence of newspapers, as well as the more diffuse world of online political blogs \citep{Adamic2005,Gentzkow2010}. \cite{Lin2011} provide a good example of a study which makes extensive use of automated content analysis - a necessity arising from its dataset of 66830 blog posts and 57221 online news articles. The authors estimate the political slant of these entities by counting the frequencies with which politicians of either side are mentioned and determine that blogs are generally more biased. Unfortunately for us, the authors don't go into the details of their text analysis, and offer no information on the acquisition and pre-processing of the data.
%Another well-known example fitting into this area of study is the set of studies conducted by King et al. \citep{KING2013,King2014,KING2017}, in which the authors study censorship by the country's government on its lively blogosphere. However, the authors also provide no information on how their data was collected ``our extensive engineering effort, which we do not detail here for obvious reasons [...]''.

The websites of politicians and their parties have also been the object of research. Researchers have found that in order to identify the constituencies, motives, and modes of communication among these actors, their websites can be very illuminating sources of information \citep{Druckman2009,Druckman2010,Cryer2017,Esterling2011,Esterling2011a,Norris2003,Therriault2010}. \cite{Druckman2009,Druckman2010} rely on the \textit{National Journal} to find the websites, then hand-coded them. \cite{Cryer2017} mentions that she relied on Archive-it, a web service of the Internet Archive. Though the Internet Archive may provide extensive coverage of high profile officials or national governments, we found that its coverage of municipal government websites was sparse and irregular.
\cite{Esterling2011,Esterling2011a} rely on hand-coded data by the Congressional Management Foundation, a nonprofit organization which aims to assist Congress. \cite{Therriault2010} use automated text analysis, and also has the most extensive overview of the associated methodology. However, the division of the website into sections (home page, topics, issues, details) is done by hand. The author acquired the websites from the Library of Congress (which only collected them from legislators who actually consented, and Therriault notes that this causes nonrandom missingness).

@@

We have developed a methodological pipeline for automatically gathering and preparing government websites for comparative content analysis. This methodology holds the potential to vastly scale up the data collection efforts underpinning the growing body of research that is focused on government website analysis. The methods involved in the pipeline include checking the integrity of the site addresses, extracting English language from website contents, identifying document types, and removing boilerplate language. Government website contents can, and have been, used to study questions related representation, government transparency, and public policy priorities. The methods we develop can be used to scale up projects involving website data collection by automating the process. Through an application to the analysis of municipal websites in six different states, we show how our pipeline is capable of gathering corpora that shed light on the forms and functions of local government. We find that government website contents are associated with the partisanship of the mayor in ways that would be expected based on the parties' national priorities and past research on the effects of mayoral partisanship on city governments.

We offer several contributions that will be valuable in future research endeavors. First, the data collected in the current study can be used for comparative analysis of US city website contents. Second, the pipeline we present can be used as a set of procedures to follow in gathering large-scale datasets of textual contents from other samples of governments. For example, the pipeline we have developed could be used to build comparative datasets of state or federal bureaucratic agencies. Third, our findings regarding the effects of mayoral partisanship on city website contents advance the literature on the role of partisan leadership in local government, and reinforce the finding of \citet{gerber2011mayors} that the effects of mayoral partisanship can be best observed through the analysis of domains of government (e.g., website contents) that are not heavily constrained by state or national governments.
